Effects of the body force on the pedestrian and the evacuation dynamics

### 2020-03-05 paper.tex
agregue dibujo de la puerta en bottleneck
agregue parrafo de unidades

@@

\caption[width=0.47\columnwidth]{Snapshots of the contact networks of a 225
pedestrian evacuation through a bottleneck. The door is placed at
$(x,y)=(20,10)\,$m, the width of the door is 0.92$\,$m (equivalent to 2
pedestrian\textsc{\char13}s diameter). The lines that connect the nodes
(pedestrians) represent the contact between them. The color represents the
degree (the number of pedestrians with which it is connected). (a) and (b)
correspond to a simulation without body force with $v_d=$2 and $v_d=$10
respectively. (c) and (d) correspond to simulations with $k_n=1.2\,$E6 with
$v_d=$2 and $v_d=$10 respectively. Color online only.}
\label{network_bottleneck}
 \end{figure}

>>>>

We warn the reader that, for simplicity, we will not include the units
corresponding to the numerical results. Remember that the friction coefficient
has units $\left [ k_t \right]=$Kg~m$^{-1}$~s$^{-1}$, 
the body stiffness coefficient $\left [ k_n \right]=$Kg~s$^{-2}$, 
the density $\left [ \rho \right]=$p~m$^{-2}$ and the flow $\left [ J \right
]=$p~m$^{-1}$~s$^{-1}$.\\

@@

\caption[width=0.47\columnwidth]{Snapshots of the contact networks of a 225
pedestrian evacuation through a bottleneck. The door is placed at
$(x,y)=(20,10)\,$m, the width of the door is 0.92$\,$m (equivalent to 2
pedestrian\textsc{\char13}s diameter). The lines that connect the nodes
(pedestrians) represent the contact between them. The color represents the
degree (the number of pedestrians with which it is connected). (a) and (b)
correspond to a simulation without body force with $v_d=$2 and $v_d=$10
respectively. (c) and (d) correspond to simulations with $k_n=1.2\,$E6 with
$v_d=$2 and $v_d=$10 respectively. The black rectangle at the right
represents the exit door. Color online only.}
\label{network_bottleneck}
 \end{figure}
